### 2018-04-19 Manuscript/chapter4.tex
Mortality ANOVA description

We reanalyzed our previously published dataset with a subset more relevant to our RNA-sequencing approaches in the current study that have a more focused question regarding diet quality. We briefly show it again here to inform the RNA-seq comparison because we reduced the number of treatments (from eight to four) from the original published data (\citealt{adamInt}). When statistically analyzing the subset of this data that was used for RNA-sequencing analysis, we found that the mortality rates across diet quality and virus exposure at least numerically retained the same trends (Figure \ref{fig:4panels}).

Mortality rates of honeybees 72 hour post-inoculation differed (or did not?) among the treatment groups (mixed model ANOVA across all treatment groups, df=@@@, @@@; F=@@@; p<@@@). The effect of virus treatment (mixed model ANOVA, df=@@@, @@@; F=@@@; p<@@@), diet treatment (mixed model ANOVA, df=@@@,@@@; F=@@@; p<@@@), and interaction between the two factors (mixed model ANOVA, df=@@@, @@@; F=@@@, p=@@@) did (or did not?) differ. The virus treatment was significant: For a given diet, honeybees exposed to the virus showed significantly higher mortality rate than honeybees not exposed to the virus (Tukey HSD, p<0.05). Without virus exposure, there was only an intermediate reduction in mortality rate for bees fed Castanea pollen? (Tukey HSD, p>0.05). However, with virus exposure, there was a significant reduction in mortality rate for beeds fed Castanea pollen (Tukey HSD, p<0.05). Overall, we discovered that the higher-quality Castanea diet had the ability to significantly reduce mortality in the presence of IAPV infection compared to the lower-quality Cistus diet (Figure \ref{fig:4panels}).

Comment on (Figure \ref{fig:4panels}) @@@

\begin{figure}[H]
\centering
  \begin{framed}
  \includegraphics[width=0.8\textwidth]{Images/4panels}
  \end{framed}
  \caption{Mortality rates for all cages, mortality rates for subset of honeybees used for RNA-seq, IAPV titers for all cages, IAPV titers for subset of honeybees used for RNA-seq subset.}
  \label{fig:4panels}
\end{figure}

>>>>

We reanalyzed our previously published dataset with a subset more relevant to our RNA-sequencing approaches in the current study that have a more focused question regarding diet quality. We briefly show it again here to inform the RNA-seq comparison because we reduced the number of treatments (from eight to four) from the original published data (\citealt{adamInt}).

Mortality rates of honeybees 72 hour post-inoculation significantly differed among the treatment groups (mixed model ANOVA across all treatment groups, df=3, 55; F=10.07; p<2.18e-05). The effect of virus treatment (mixed model ANOVA, df=1, 55; F=24.343; p<7.84e-06) and diet treatment (mixed model ANOVA, df=1, 55; F=5.796; p<0.0194) were significant, but the interaction between the two factors (mixed model ANOVA, df=1, 55; F=0.062, p=0.8039) was not significant. The virus treatment was significant: For a given diet, honeybees exposed to the virus showed significantly higher mortality rate than honeybees not exposed to the virus (Tukey HSD, p<0.05). Without virus exposure, there was only a numerical reduction in mortality rate for bees fed Castanea pollen compared to Rockrose pollen (Tukey HSD, p>0.05). Similarly, with virus exposure, there was only a numerical reduction in mortality rate for beeds fed Castanea pollen compared to Rockrose pollen (Tukey HSD, p>0.05). Overall, we discovered that the higher-quality Castanea diet had the ability to numerically reduce mortality in the presence of IAPV infection compared to the lower-quality Rockrose diet (Figure \ref{fig:mortality} A).

IAPV titer volumes of honeybees 72 hour post-inoculation significantly differed among the treatment groups (mixed model ANOVA across all treatment groups, df=3, 34; F=6.096; p<0.00196). The effect of virus treatment (mixed model ANOVA, df=1, 34; F=15.686; p<0.000362) was significant, but the diet treatment (mixed model ANOVA, df=1, 34; F=1.898; p>0.05) and the interaction between the two factors (mixed model ANOVA, df=1, 34; F=0.702, p>0.05) were not significant. Honeybees that were infected with the virus and fed a poor-quality Rockrose diet showed significant increases in IAPV titer volumes compared to honeybees that were not infected with the virus regardless of their diet quality (Tukey HSD, p<0.05). Overall, we discovered that the higher-quality Castanea diet had the ability to numerically reduce IAPV titer volume for both infected and non-infected honeybees (Figure \ref{fig:mortality} B).

\begin{figure}[H]
\centering
  \begin{framed}
  \includegraphics[width=\textwidth]{Images/mortality}
  \end{framed}
  \caption{Mortality rates (A) and IAPV titers (B) for the four treatment groups.}
  \label{fig:mortality}
\end{figure}
